Growth Resilience

### 2017-06-21 analysis/analysis_resilience_bai.Rmd
update only three years

```{r}
vars <- c('disturb_year','site')
```

@@

```{r}
# Post hoc Define model
mymodel <- aov_rt$mymodel
postH_rc <- phc(mymodel = mymodel, resp_var = resp_var)
```

@@

```{r}
# Post hoc Define model
mymodel <- aov_rrs$mymodel
postH_rc <- phc(mymodel = mymodel, resp_var = resp_var)
```

@@

```{r}
# Post hoc Define model
mymodel <- aov_rs$mymodel
postH_rc <- phc(mymodel = mymodel, resp_var = resp_var)
```

>>>>

```{r}
# Only 2005 and 2012
re <- re %>% filter(disturb_year != 1995) %>% as.data.frame()
vars <- c('disturb_year','site')
```

@@

```{r}
# Post hoc Define model
mymodel <- aov_rt$mymodel
postH_rt <- phc(mymodel = mymodel, resp_var = resp_var)
```

@@

```{r}
# Post hoc Define model
mymodel <- aov_rrs$mymodel
postH_rrs <- phc(mymodel = mymodel, resp_var = resp_var)
```

@@

```{r}
# Post hoc Define model
mymodel <- aov_rs$mymodel
postH_rs <- phc(mymodel = mymodel, resp_var = resp_var)
```
